Plot curve fits

### 2023-01-05 Working Rmds/MainAnalysis.Rmd
Read in most recent CvTdb file. Specify 'new_name' = 'old_name' list for pre-processing data ensuring that 'old_name' properly refers to corrected/normalized variables as produced in 'pulling_oral_iv_data_cvtdb.Rmd': 'Dose' = 'studies.dose_level_normalized_corrected', 'LOQ' = 'series.loq_normalized', 'Value_SD' = 'conc_time_values.conc_sd_normalized'.

Read in CvTdb data pulled in `pulling_oral_iv_data_cvtdb.Rmd`.

```{r, load_cvt, eval = TRUE}
cvt_data <- fread("../inst/ext/cvt_data_2022_12_15_16_20_21.csv")
```

Run a one-compartment fit on the data, and write out the results. Timestamp the file name with the current date and time (at the beginning of the runs) in format YYYY_MM_DD_hh_mm.

@@

Fit the flat model.

@@

system.time(
    PK.fit.table.flat <- fit_all(
     data.set = cvt_data,
      model = "flat",
      modelfun = "analytic",
      names_list =list(
                      "Compound_Dosed" = "studies.test_substance_name_original",
                      "DTXSID_Dosed" = "chemicals_dosed.dsstox_substance_id",
                      "CAS_Dosed" = "chemicals_dosed.dsstox_casrn",
                      "Compound_Analyzed" = "series.analyte_name_original",
                      "DTXSID_Analyzed" = "chemicals_analyzed.dsstox_substance_id",
                      "CAS_Analyzed" = "chemicals_analyzed.dsstox_casrn",
                      "Reference" = "documents_reference.id",
                      "Extraction" = "documents_extraction.id",
                      "Species" = "subjects.species",
                      "Weight" ="subjects.weight_kg",
                      "Weight.Units" = NULL,
                      "Dose" = "studies.dose_level_normalized",
                      "Dose.Units" = NULL,
                      "Time" = "conc_time_values.time_hr",
                      "Time.Units" = NULL,
                      "Media" = "series.conc_medium_normalized",
                      "Value" = "conc_time_values.conc",
                      "Value.Units" = NULL,
                      "Route" = "studies.administration_route_normalized",
                      "LOQ" = "series.loq",
                      "Subject" = "subjects.id",
                      "N_Subjects" = "series.n_subjects_in_series",
                      "Value_SD" = "conc_time_values.conc_sd"),
                    defaults_list =   list(
                      "Weight.Units" = "kg",
                      "Dose.Units" = "mg/kg",
                      "Time.Units" = "h",
                      "Value.Units" = "mg/L"),
      ratio_conc_to_dose = 1,
                    calc_loq_factor = 0.45,
                    routes_keep = c("po", "iv"),
                    media_keep = c("blood", "plasma"),
      optimx_args = list(
                      "method" = "bobyqa",
                      "itnmax" = 1e6,
                      "control" = list("kkt" = FALSE)
                    ),
      suppress.messages = TRUE
    )
)

write.csv(PK.fit.table.flat, paste("inst/ext/PK_fit_table_flat_",
                                    timestamp,
                                    ".csv",
                                    sep=""), row.names = FALSE)

@@

Fit the 1-compartment model.

@@

### do 1-Compartment fit
system.time(
    PK.fit.table.1comp <- fit_all(
      data.set = cvt_data,
      model = "1compartment",
      modelfun = "analytic",
      names_list =list(
                      "Compound_Dosed" = "studies.test_substance_name_original",
                      "DTXSID_Dosed" = "chemicals_dosed.dsstox_substance_id",
                      "CAS_Dosed" = "chemicals_dosed.dsstox_casrn",
                      "Compound_Analyzed" = "series.analyte_name_original",
                      "DTXSID_Analyzed" = "chemicals_analyzed.dsstox_substance_id",
                      "CAS_Analyzed" = "chemicals_analyzed.dsstox_casrn",
                      "Reference" = "documents_reference.id",
                      "Extraction" = "documents_extraction.id",
                      "Species" = "subjects.species",
                      "Weight" ="subjects.weight_kg",
                      "Weight.Units" = NULL,
                      "Dose" = "studies.dose_level_normalized",
                      "Dose.Units" = NULL,
                      "Time" = "conc_time_values.time_hr",
                      "Time.Units" = NULL,
                      "Media" = "series.conc_medium_normalized",
                      "Value" = "conc_time_values.conc",
                      "Value.Units" = NULL,
                      "Route" = "studies.administration_route_normalized",
                      "LOQ" = "series.loq",
                      "Subject" = "subjects.id",
                      "N_Subjects" = "series.n_subjects_in_series",
                      "Value_SD" = "conc_time_values.conc_sd"),
                    defaults_list =   list(
                      "Weight.Units" = "kg",
                      "Dose.Units" = "mg/kg",
                      "Time.Units" = "h",
                      "Value.Units" = "mg/L"),
      ratio_conc_to_dose = 1,
                    calc_loq_factor = 0.45,
                    routes_keep = c("po", "iv"),
                    media_keep = c("blood", "plasma"),
      optimx_args = list(
                      "method" = "bobyqa",
                      "itnmax" = 1e6,
                      "control" = list("kkt" = FALSE)
                    ),
      suppress.messages = TRUE
  )
)

@@

Fit the 2-compartment model.

```{r, run_invivoPKfit_2comp}
### do 2-Compartment fit
system.time(
    PK.fit.table.2comp <- fit_all(
      data.set = cvt_data,
      model = "2compartment",
      modelfun = "analytic",
      names_list =list(
                      "Compound_Dosed" = "studies.test_substance_name_original",
                      "DTXSID_Dosed" = "chemicals_dosed.dsstox_substance_id",
                      "CAS_Dosed" = "chemicals_dosed.dsstox_casrn",
                      "Compound_Analyzed" = "series.analyte_name_original",
                      "DTXSID_Analyzed" = "chemicals_analyzed.dsstox_substance_id",
                      "CAS_Analyzed" = "chemicals_analyzed.dsstox_casrn",
                      "Reference" = "documents_reference.id",
                      "Extraction" = "documents_extraction.id",
                      "Species" = "subjects.species",
                      "Weight" ="subjects.weight_kg",
                      "Weight.Units" = NULL,
                      "Dose" = "studies.dose_level_normalized",
                      "Dose.Units" = NULL,
                      "Time" = "conc_time_values.time_hr",
                      "Time.Units" = NULL,
                      "Media" = "series.conc_medium_normalized",
                      "Value" = "conc_time_values.conc",
                      "Value.Units" = NULL,
                      "Route" = "studies.administration_route_normalized",
                      "LOQ" = "series.loq",
                      "Subject" = "subjects.id",
                      "N_Subjects" = "series.n_subjects_in_series",
                      "Value_SD" = "conc_time_values.conc_sd"),
                    defaults_list =   list(
                      "Weight.Units" = "kg",
                      "Dose.Units" = "mg/kg",
                      "Time.Units" = "h",
                      "Value.Units" = "mg/L"),
      ratio_conc_to_dose = 1,
                    calc_loq_factor = 0.45,
                    routes_keep = c("po", "iv"),
                    media_keep = c("blood", "plasma"),
      optimx_args = list(
                      "method" = "bobyqa",
                      "itnmax" = 1e6,
                      "control" = list("kkt" = FALSE)
                    ),
      suppress.messages = TRUE
    )
)

>>>>

# Read in CvTdb data

Read in CvTdb data that was pulled and normalized in `pulling_oral_iv_data_cvtdb.Rmd`.

```{r, load_cvt, eval = TRUE}
cvt_data <- fread("../inst/ext/cvt_data_2023_01_05_09_37_22.csv")
```

# Setup for model fitting

## Timestamp
Timestamp the file name with the current date and time (at the beginning of the runs) in format YYYY_MM_DD_hh_mm.

@@

## Settings for pre-processing data

List of new_name = old_name to supply for preprocessing data

```{r}
names_list <- list(
  "Compound_Dosed" = "studies.test_substance_name_original",
  "DTXSID_Dosed" = "chemicals_dosed.dsstox_substance_id",
  "CAS_Dosed" = "chemicals_dosed.dsstox_casrn",
  "Compound_Analyzed" = "series.analyte_name_original",
  "DTXSID_Analyzed" = "chemicals_analyzed.dsstox_substance_id",
  "CAS_Analyzed" = "chemicals_analyzed.dsstox_casrn",
  "Reference" = "documents_reference.id",
  "Extraction" = "documents_extraction.id",
  "Species" = "subjects.species",
  "Weight" ="subjects.weight_kg",
  "Weight.Units" = NULL,
  "Dose" = "studies.dose_level_normalized_corrected", #note that dose levels were corrected in pulling_oral_iv_data_cvtdb.Rmd
  "Dose.Units" = NULL,
  "Time" = "conc_time_values.time_hr",
  "Time.Units" = NULL,
  "Media" = "series.conc_medium_normalized",
  "Value" = "conc_time_values.conc", #already normalized to mg/L units in CvTdb
  "Value.Units" = NULL,
  "Route" = "studies.administration_route_normalized",
  "LOQ" = "series.loq_normalized", #note that LOQs were normalized to mg/L units in pulling_oral_iv_data_cvtdb.Rmd
  "Subject" = "subjects.id",
  "N_Subjects" = "series.n_subjects_in_series",
  "Value_SD" = "conc_time_values.conc_sd_normalized" #note that SDs were normalized to mg/L units in pulling_oral_iv_data_cvtdb.Rmd
  )
```

List of default values for new columns added in preprocessing data

```{r}
defaults_list <- list(
                      "Weight.Units" = "kg",
                      "Dose.Units" = "mg/kg",
                      "Time.Units" = "h",
                      "Value.Units" = "mg/L")
```

# Model fitting

## Flat model

@@

system.time(
  PK.fit.table.flat <- fit_all(
    data.set = cvt_data,
    model = "flat",
    modelfun = "analytic",
    names_list = names_list,
    defaults_list =  defaults_list,
    ratio_conc_to_dose = 1,
    calc_loq_factor = 0.45,
    routes_keep = c("po", "iv"),
    media_keep = c("blood", "plasma"),
    optimx_args = list(
      "method" = "bobyqa",
      "itnmax" = 1e6,
      "control" = list("kkt" = FALSE)
    ),
    suppress.messages = TRUE
  )
)

write.csv(PK.fit.table.flat, paste("../inst/ext/PK_fit_table_flat_",
                                    timestamp,
                                    ".csv",
                                    sep=""), row.names = FALSE)

@@

## 1-compartment model

@@

### do 1-Compartment fit
system.time(
    PK.fit.table.1comp <- fit_all(
      data.set = cvt_data,
      model = "1compartment",
      modelfun = "analytic",
        names_list = names_list,
    defaults_list =  defaults_list,
      ratio_conc_to_dose = 1,
                    calc_loq_factor = 0.45,
                    routes_keep = c("po", "iv"),
                    media_keep = c("blood", "plasma"),
      optimx_args = list(
                      "method" = "bobyqa",
                      "itnmax" = 1e6,
                      "control" = list("kkt" = FALSE)
                    ),
      suppress.messages = TRUE
  )
)

@@

## 2-compartment model

```{r, run_invivoPKfit_2comp}
### do 2-Compartment fit
system.time(
    PK.fit.table.2comp <- fit_all(
      data.set = cvt_data,
      model = "2compartment",
      modelfun = "analytic",
          names_list = names_list,
    defaults_list =  defaults_list,
      ratio_conc_to_dose = 1,
                    calc_loq_factor = 0.45,
                    routes_keep = c("po", "iv"),
                    media_keep = c("blood", "plasma"),
      optimx_args = list(
                      "method" = "bobyqa",
                      "itnmax" = 1e6,
                      "control" = list("kkt" = FALSE)
                    ),
      suppress.messages = TRUE
    )
)

### 2023-01-05 Working Rmds/plot_fits.Rmd
Read in most recent CvTdb file. Specify 'new_name' = 'old_name' list for pre-processing data ensuring that 'old_name' properly refers to corrected/normalized variables as produced in 'pulling_oral_iv_data_cvtdb.Rmd': 'Dose' = 'studies.dose_level_normalized_corrected', 'LOQ' = 'series.loq_normalized', 'Value_SD' = 'conc_time_values.conc_sd_normalized'.

@@

```{r}
cvt <- preprocess_data(data.set = cvt_data,
                       names_list =list(
                       "Compound_Dosed" = "studies.test_substance_name_original",
                              "DTXSID_Dosed" = "chemicals_dosed.dsstox_substance_id",
                              "CAS_Dosed" = "chemicals_dosed.dsstox_casrn",
                              "Compound_Analyzed" = "series.analyte_name_original",
                              "DTXSID_Analyzed" = "chemicals_analyzed.dsstox_substance_id",
                              "CAS_Analyzed" = "chemicals_analyzed.dsstox_casrn",
                      "Reference" = "documents_reference.id",
                      "Extraction" = "documents_extraction.id",
                      "Species" = "subjects.species",
                      "Weight" ="subjects.weight_kg",
                      "Weight.Units" = NULL,
                      "Dose" = "correct.dose_level_normalized",
                      "Dose.Units" = NULL,
                      "Time" = "conc_time_values.time_hr",
                      "Time.Units" = NULL,
                      "Media" = "series.conc_medium_normalized",
                      "Value" = "conc_time_values.conc",
                      "Value.Units" = NULL,
                      "Route" = "studies.administration_route_normalized",
                      "LOQ" = "series.loq_normalized",
                      "Subject" = "subjects.id",
                              "N_Subjects" = "series.n_subjects_in_series",
                              "Value_SD" = "conc_time_values.conc_sd"),
                    defaults_list =   list(
                      "Weight.Units" = "kg",
                      "Dose.Units" = "mg/kg",
                      "Time.Units" = "h",
                      "Value.Units" = "mg/L"),
      ratio_conc_to_dose = 1,
                    calc_loq_factor = 0.45,
                    routes_keep = c("po", "iv"),
                    media_keep = c("blood", "plasma"),
      suppress.messages = FALSE)
```

```{r, read_data}
### this block reads the exported model fit csv files from run_invivoPKfit

PK.fit.table.1comp <- fread(paste0("inst/ext/", "PK_fit_table_1comp_2022_12_08_09_44_34.csv",sep=""))
PK.fit.table.2comp <- fread(paste0("inst/ext/", "PK_fit_table_2comp_2022_12_08_10_31_09.csv",sep=""))
PK.fit.table.flat <- fread(paste0("inst/ext/", "PK_fit_table_flat_2022_12_08_12_03_24.csv",sep=""))

@@

Get a table of the winning model for each dataset (minimum AIC).

```{r}
tmp <- unique(pk_fit[, .(DTXSID, Species, Analysis_Type, model, AIC)])
setorder(tmp, DTXSID, Species, Analysis_Type, AIC, na.last = TRUE)
model_win <- tmp[, .(winmodel = model[1]), by = .(DTXSID, Species, Analysis_Type)]
pk_fit <- model_win[pk_fit, on = c("DTXSID", "Species", "Analysis_Type")]
pk_fit[, winning:=(model == winmodel)]

@@

#plot all models
tmp <- mapply(plot_fit,
              DTXSID_in = plot_table$DTXSID,
                     Species_in = plot_table$Species,
              MoreArgs = list(
                     model_in = "all",
                     Analysis_Type_in = "Joint",
                     DF = DF,
                     pk_fit = pk_fit,
                     n = 101,
                     log10_scale_time = FALSE,
                     file_path = "inst/ext/plots/Joint Analysis/model_all/")
                     )

@@

>>>>

Read in CvTdb data pulled in `pulling_oral_iv_data_cvtdb.Rmd`.

```{r, load_cvt, eval = TRUE}
cvt_data <- fread("../inst/ext/cvt_data_2023_01_05_09_37_22.csv")
```

@@

```{r}
cvt <- preprocess_data(data.set = cvt_data,
                       names_list =list(
                         "Compound_Dosed" = "studies.test_substance_name_original",
                         "DTXSID_Dosed" = "chemicals_dosed.dsstox_substance_id",
                         "CAS_Dosed" = "chemicals_dosed.dsstox_casrn",
                         "Compound_Analyzed" = "series.analyte_name_original",
                         "DTXSID_Analyzed" = "chemicals_analyzed.dsstox_substance_id",
                         "CAS_Analyzed" = "chemicals_analyzed.dsstox_casrn",
                         "Reference" = "documents_reference.id",
                         "Extraction" = "documents_extraction.id",
                         "Species" = "subjects.species",
                         "Weight" ="subjects.weight_kg",
                         "Weight.Units" = NULL,
                         "Dose" = "studies.dose_level_normalized_corrected", #note that dose levels were corrected in pulling_oral_iv_data_cvtdb.Rmd
                         "Dose.Units" = NULL,
                         "Time" = "conc_time_values.time_hr",
                         "Time.Units" = NULL,
                         "Media" = "series.conc_medium_normalized",
                         "Value" = "conc_time_values.conc", #already in mg/L units
                         "Value.Units" = NULL,
                         "Route" = "studies.administration_route_normalized",
                         "LOQ" = "series.loq_normalized", #note that LOQs were normalized to mg/L units in pulling_oral_iv_data_cvtdb.Rmd
                         "Subject" = "subjects.id",
                         "N_Subjects" = "series.n_subjects_in_series",
                         "Value_SD" = "conc_time_values.conc_sd_normalized" #note that SDs were normalized to mg/L units in pulling_oral_iv_data_cvtdb.Rmd
                         ),
                       defaults_list =   list(
                         "Weight.Units" = "kg",
                         "Dose.Units" = "mg/kg",
                         "Time.Units" = "h",
                         "Value.Units" = "mg/L"),
                       ratio_conc_to_dose = 1,
                       calc_loq_factor = 0.45,
                       routes_keep = c("po", "iv"),
                       media_keep = c("blood", "plasma"),
                       suppress.messages = FALSE)
cvt <- as.data.table(cvt)
```

Read in the fitted model parameter values.

```{r, read_data}
timestamp <- "2023_01_04_10_56"
PK.fit.table.1comp <- fread(paste0("../inst/ext/", "PK_fit_table_1comp_", timestamp, ".csv",sep=""))
PK.fit.table.2comp <- fread(paste0("../inst/ext/", "PK_fit_table_2comp_", timestamp, ".csv",sep=""))
PK.fit.table.flat <- fread(paste0("../inst/ext/", "PK_fit_table_flat_", timestamp, ".csv",sep=""))

@@

Get a table of the winning model for each dataset (the one with minimum AIC).

```{r}
tmp <- unique(pk_fit[, .(DTXSID, Species, Analysis_Type, References.Analyzed, model, AIC)])

#sort AIC from smallest to largest within each dataset, putting NAs last
setorder(tmp, DTXSID, Species, Analysis_Type, References.Analyzed, AIC, na.last = TRUE)
#the winning model will now be listed first within each dataset (smallest AIC)
model_win <- tmp[, .(winmodel = model[1]), by = .(DTXSID, Species, Analysis_Type, References.Analyzed)]
pk_fit <- model_win[pk_fit, on = c("DTXSID", "Species", "Analysis_Type", "References.Analyzed")]
pk_fit[, winning:=(model == winmodel)]

@@

#plot all models
tmp <- mapply(plot_fit,
              DTXSID_in = plot_table$DTXSID,
                     Species_in = plot_table$Species,
              MoreArgs = list(
                     model_in = "all",
                     Analysis_Type_in = "Joint",
                     DF = cvt,
                     pk_fit = pk_fit,
                     n = 101,
                     limit_y_axis = FALSE,
                     log10_scale_y = FALSE,
                     plot_errbars = TRUE,
                     log10_scale_time = FALSE,
                     file_path = "../inst/ext/plots/Joint Analysis/model_all/")
                     )

@@

Problem: DTXSID0022985_rat_Joint_all does not plot any model lines. Why?

```{r}
pk_fit[DTXSID %in% "DTXSID0022985"]
```

Apparently there were no detected data points?

```{r}
cvt[DTXSID %in% "DTXSID0022985", .(Reference, Value, LOQ)]
```

Hmm. Something is very weird here. I definitely see some detected points. They are all the same reference, so it isn't that a single-reference fit did not work but a joint fit did work.
